The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes in ground-based coronagraphs

### 2021-05-26 response.txt

"For the SI controller, improving seeing (larger $r_0$) reduces speckle lifetime.  As the turbulence power is reduced, the control system is better able to reject low temporal frequencies, resulting in lower speckle lifetimes.  As with $D$ and $\mathcal{V}$, the LP controller shows little variation in lifetimes vs. $r_0$.  Here again, the predictive controller whitens the noise to the same floor set by photon noise, which produces an output PSD of roughly the same shape resulting in similar speckle lifetimes.  The lifetime increases somewhat vs $r_0$ on the larger diameters as the turbulence power becomes relatively lower compared to photon noise, resulting in reduced effectiveness of the predictor such that more correlations remain in the output."

----------------------------------------------

Section 7
Comment: This section is based on the supposition that "we have a technique for measuring the
Legendre mode coefficients an." It is difficult to evaluate the usefulness of this discussion
without understanding the prospects for making such measurements. Perhaps the authors could
weigh in on how or whether the mode coefficients could be measured with current or future
instruments.

Response: We have added a brief introduction to AO PSF reconstruction, and provided an outline of the basic algorithm needed to perform reconstruction
for high-contrast imaging.  The new text reads:

The reconstruction of the post-AO PSF using AO system telemetry has been studied
for some time, primarily focused on the long-exposure PSF, e.g. Veran et al. (1997)
and see the recent review by Beltramo-Martin et al. (2020). PSF reconstruction in the
context of high-contrast imaging is typically based on image data alone (Marois et al.
2006; Lafrenière et al. 2007), however the potential for telemetry-based PSF estimation
in high-contrast imaging has been recognized (Frazin 2013; Codona & Kenworthy 2013).
Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph
to analyze the performance of PSF estimation and subtraction. We are particularly
motivated by the use of WFS telemetry to improve on the sensitivity limit set by
atmospheric speckle lifetimes, however this analysis could be applied to conventional
post-processing such as the KLIP algorithm (Soummer et al. 2012).

A closed-loop wavefront control system measures the coefficients of the controlled
modes in the residual wavefront at each loop time step. The WFS produces mea-
surements of the residual phase with modal coefficients ∆hpmn(t) which we assume are
recorded. Additionally we assume that focal plane intensity is recorded with a detector
reading out at the same rate as and synchronized to the WFS, such that measurements
Imn (t) are recorded at each pixel. The measured focal plane intensity may include signal
from a planet in addition to scattered starlight.

At some later time we use the measured residual coefficients to reconstruct an estimate
of the focal plane intensity due to scattered starlight alone. To begin, we reconstruct
the residual phase based on Equation 28

\Delta\Phi(\vec{q},t) = \frac{2\pi}{\lambda} \sum\limits_{mn} \left[ \Delta h_{mn}^{+}(t) M_{mn}^{+}(\vec{q}) + \Delta h_{mn}^{-}(t) M_{mn}^{-}(\vec{q})\right].

We then propagate the residual phase to the focal plane

\hat{I}(\vec{r},t) = G \left\{\mathcal{A}(\vec{q}) \mbox{e}^{i\Delta\Phi(\vec{q},t)} \right\}

where A(~q) defines the pupil and G{·} is the system propagation operator, which could
include information such as the effect of the coronagraph, non-common path aberrations
(not sensed by the WFS which measures the ∆hpmn (t)), and Fresnel propagation. See
Herscovici-Schiller et al. (2017) for an example of the construction of such a model.
In the case of the perfect coronagraph and ideal optical system used in this work,
the propagation operator reduces to Equation 29. The result of applying G{·} to the
reconstructed wavefront is an estimated intensity time series at position ~rmn

\hat{I}_{mn}(t) = \hat{I}(\vec{r}_{mn},t)

In Section 3 we developed the expansion of the intensity time-series in terms of orthonormal Legen-
dre polynomials Pη . For a segment of the reconstructed intensity of length T, we measure
the coefficients of the Legendre polynomials

\hat{a}_\eta = \int_{-1}^1 \hat{I}_{mn}\left(\frac{T}{2}\xi\right) P_\eta(\xi) d\xi.

We then subtract the first $N$ Legendre modes of the reconstructed time-series from the measured focal plane intensity time-series, giving the ``post-processed'' intensity

I_{mn,pp}(t) = I_{mn}(t) - \sum_{\eta=0}^{\eta=N-1} \hat{a}_\eta P_\eta\left(\frac{2}{T}t\right).

@@

Section 9
"We have shown that the speckle lifetime is an order of magnitude shorter than previous studies
have found"
Comment: Unless I'm mistaken, this point was not explicitly made in the body of the paper.

Response: This point was not made explicity.  We added the following paragraph at the end of Section 5.4:

"For comparison, the ``crossing-time'' speckle lifetime of \citet{2005SPIE.5903..170M} would be $\tau=0.3D/\mathcal{V} = 224$ ms for the turbulence averaged windspeed used in these calculations, with the caveat that the constant of propotionality is expected to vary with coronagraph. We find lifetimes much shorter than this, up to a factor of 10 shorter for the LP controller. Figures \ref{fig:lifetime_2Dcomp} and \ref{fig:lifetime_radprof} show that speckle lifetime has a strong dependence on control law, and varies with position in the image.  We investigate the $D/\mathcal{V}$ scaling next."
----------------------------------------------

Other changes:
Abstract: For brevity deleted the sentence "The temporal correlation of speckles reduces sensitivity as they average much more slowly than photon noise."

Notation: changed the Legendre polynomial index from n to \eta to avoid confusion with the spatial frequency index

A few minor typos were corrected.

### 2021-05-26 specklelives.tex
merged
updated

Next, we analyze the change in speckle lifetime with guide star brightness, telescope diameter, wind speed, and seeing.   We held relative spatial frequency constant with $D$, such that the resultant speckle occurs at the same relative projected separation in $\lambda/D$ units.  This compares the performance of coronagraphic AO systems given the improvement in spatial resolution with $D$.  \textbf{Note that the input power per Fourier mode scales as $D^{-2}$, that is it will be lower given larger $D$.  This means that the input temporal PSD has a different shape due to relative spatial frequency as well as different power due to both the wind speed and diameter. The input noise PSD will also be lower for each mode, but by $D^{-1}$ since the signal to noise ratio goes as S/N $\propto \sqrt{D}$.  The balance betwen these inputs can be expected to affect the performance of the optimized controllers, resulting in variation in speckle lifetimes.}

@@

\subsection{Post-Processing}
The temporal decorrelation of speckle noise is one of the main benefits of PSF-subtraction post-processing \citep{2006ApJ...641..556M,2008ApJ...673..647M}, even though algorithms have typically focused on exploiting spatial correlations.  Recently, studies have begun to consider the time-domain in post-processing explicitly \citep{2021A&A...646A..24S}, and several algorithms show promise in exploiting short exposure focal-plane data \citep{2019PASP..131k4506W, 2021arXiv210306898S} and WFS telemetry \textbf{\citep[][submitted]{2021arXiv210506589R}\citep[][submitted]{2021arXiv210506590F}} to estimate speckle intensity.   Knowledge of the intensity PSD allows for such algorithms to be analyzed efficiently.  We demonstrate this by considering the prospect of telemetry-based reconstruction of the speckle time-series. \textbf{The algorithm we outlined made} use of the main WFS images, but other information sources such as accelerometers, low-order WFS telemetry, and environmental sensors could be used.  \textbf{The key challenge is in the construction of the system propagation model.}  We used the temporal intensity PSDs to predict the sensitivity gain possible \textbf{if this can be done}.  If the first few low-order temporal modes, here described in terms of the Legendre polynomials, can be determined and subtracted from the intensity in the focal plane, large improvements in exposure time are possible.  The fact that only a few low-order temporal modes need to be reconstructed has the important consequence that any such post-processing algorithm does not need to accurately determine the intensity at every time interval, and does not need to be perfect.  Accuracy in the mean, slope, and other low-order terms of a few percent is all that is needed to make these gains.

>>>>

Next, we analyze the change in speckle lifetime with guide star brightness, telescope diameter, wind speed, and seeing.   We held relative spatial frequency constant with $D$, such that the resultant speckle occurs at the same relative projected separation in $\lambda/D$ units.  This compares the performance of coronagraphic AO systems given the improvement in spatial resolution with $D$.  \textbf{Note that the input power per Fourier mode scales as $D^{-2}$, that is it will be lower given larger $D$.  This means that the input temporal PSD has a different shape due to relative spatial frequency as well as different power due to both the wind speed and diameter. The input noise PSD will also be lower for each mode.  The balance betwen these inputs can be expected to affect the performance of the optimized controllers, resulting in variation in speckle lifetimes.}

@@

\subsection{Post-Processing}
The temporal decorrelation of speckle noise is one of the main benefits of PSF-subtraction post-processing \citep{2006ApJ...641..556M,2008ApJ...673..647M}, even though algorithms have typically focused on exploiting spatial correlations.  Recently, studies have begun to consider the time-domain in post-processing explicitly \citep{2021A&A...646A..24S}, and several algorithms show promise in exploiting short exposure focal-plane data \citep{2019PASP..131k4506W, 2021arXiv210306898S} and WFS telemetry \textbf{\citep[][submitted]{2021arXiv210506589R}\citep[][submitted]{2021arXiv210506590F}} to estimate speckle intensity.   Knowledge of the intensity PSD allows for such algorithms to be analyzed efficiently.  We demonstrate this by considering the prospect of telemetry-based reconstruction of the speckle time-series. \textbf{The algorithm we outlined made} use of the main WFS images, but other information sources such as accelerometers, low-order WFS telemetry, and environmental sensors could be used.  \textbf{The key challenge is in the construction of the system propagation model.}  We used the temporal intensity PSDs to predict the sensitivity gain possible \textbf{if this can be done}.  If the first few low-order temporal modes, here described in terms of the Legendre polynomials, can be determined and subtracted from the intensity in the focal plane, large improvements in exposure time are possible.  The fact that only a few low-order temporal modes need to be reconstructed has the important consequence that any such post-processing algorithm does not need to accurately determine the intensity at every time interval, and does not need to be perfect.  Accuracy in the mean, slope, and other low-order terms of a few percent is all that is needed to \textbf{lower the speckle lifetime and therefore increase sensitivity}.
